This is an example of article title

### 2024-09-03 paper/paper.tex
Update the statement of need section to clarify the audience of the package

The initial intention in developing the package was to simplify the process of implementing new material models within the Julia ecosystem.
In contrast to \texttt{Peridigm}, installing and extending \texttt{Peridynamics.jl} is straightforward, as it benefits from the Julia ecosystem.
\texttt{Peridynamics.jl} was already used in numerous publications \cite{Friebertshaeuser2022PAMM,Friebertshaeuser2022AIMS,Partmann2023IJF,Partmann2024AAM,Partmann2024PAMM,Tornquist2022PAMM}, which shows the practical usability of the package.

>>>>

Installing and extending \texttt{Peridynamics.jl} is straightforward, as it benefits from the Julia ecosystem.
Due to its extendability via multiple-dispatch, the package is attractive to researchers developing new peridynamic models.
\texttt{Peridynamics.jl} was already used in numerous publications \cite{Friebertshaeuser2022PAMM,Friebertshaeuser2022AIMS,Partmann2023IJF,Partmann2024AAM,Partmann2024PAMM,Tornquist2022PAMM}, which shows the practical usability of the package.

Furthermore, practitioners interested in high-performance computing can also use the default methods of the package for exciting simulations.
The package is used for teaching and was already used by several students for their final thesis.
